Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
methods is not mathematically motivated

\begin{abstract} In this work, we propose a simple and mathematically
motivated method for the problem of connectome inference in calcium imaging
data. The proposed algorithm is made of two steps. First, processing the raw
signals to detect neural peak activities. Second, inferring the degree of
association between neurons from partial correlation statistics. This paper
summarizes the methodology that led us to win the Connectomics Challenge,
proposes a simplified version of our method and finally discusses our results
with respect to other inference methods. \end{abstract}

>>>>

\begin{abstract} In this work, we propose a simple, but yet efficient,
methodologically motivated method for the problem of connectome inference in
calcium imaging data. The proposed algorithm is made of two steps. First,
processing the raw signals to detect neural peak activities. Second, inferring
the degree of association between neurons from partial correlation statistics.
This paper summarizes the methodology that led us to win the Connectomics
Challenge, proposes a simplified version of our method and finally discusses
our results with respect to other inference methods.\end{abstract}
